Implicit yaddayadda

### 2011-10-11 papers/PLDI2012/implicitization.tex
static analysis

>>>>

\emph{Widening-accelerated Kleene iterations} proceed by replacing $\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p)$ by $\abstr{x}_{p'} \widening (\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p))$ where $\widening$ is a \emph{widening operator}: for all $\abstr{x},\abstr{y}$, $\gamma(\abstr{y}) \subseteq \gamma(\abstr{x} \widening \abstr{y})$, and there exists no sequence $\abstr{u}_1,\abstr{u}_2,\dots$ of the form $\abstr{u}_{n+1} = \abstr{u}_n \widening \abstr{v}_n$ where $\abstr{v}_n$ is another sequence.
Such iterations necessarily lead to a stationary $(\abstr{x}_p)_{p \in P}$, which define an inductive invariant $(\gamma(\abstr{x}_p))_{p \in P}$. Note that this invariant is not, in general, the least one expressible in the abstract domain, and may depend on the iteration ordering (the successive choices~$p,p'$).
